### 2020-04-24 Paper/paper.tex
Added weight visualization for conv net and combined code into one file
Minor paper fixes and added text for new weight figures

We chose one of the 62 pairs of galaxies and pulled the associated data. This set consisted of 1294 grayscale model images in .png format and their associated human scores in a text file. The set was already sorted in descending order by score. However, we realized that this data was heavily skewed towards worse models, with more than half of the models having scores below 0.10. In an effort to combat overfitting on bad model images, we used only the first 600 images, which, while still skewed towards worse models (see Fig. \ref{distribution.png}), presented a much more evenly distributed data set.

@@

@@

@@

Another factor to consider is the noise associated with the human scores. As a citizen scientist project, the models in the Galaxy Zoo: Mergers data set we ranked by people with minimal training. There are also no checks in place to prevent against people clicking though models without consideration, artificially inflating or deflating their scores. We must also acknowledge the randomness of the tournament system. It is entirely possible that some models were "unlucky" and went against rounds of exclusively good models, causing them to be scored lower than they actually should have or vice versa.

@@

Future work could pertain to the expansion of the the convolutional nets to include more layers. Training with these extra layers and units would necessitate a larger data set, hopefully with a more even distributionn of model quality. We believe that such a net would obtain better results than either of the nets described in this paper.  Also, the nets we created for this paper could be applied to the other 61 galaxy pairs, and, with enough training, possibly eliminate the need for human rankings in the first place. This would allow for new models to be created and scored much faster than they have been previously.

>>>>

We chose one of the 62 pairs of galaxies and pulled the associated data. This set consisted of 1294 grayscale model images in .png format and their associated human scores in a text file. The set was already sorted in descending order by score. However, we realized that this data was heavily skewed towards worse models, with more than half of the models having scores below 0.10. In an effort to combat overfitting on bad model images, we used only the first 600 images, which, while still skewed towards worse models (see Fig. \ref{fig:distribution}), presented a much more evenly distributed data set.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.75\linewidth]{./Images/singleWeights.png}}
\caption{Visualization of weights for the single layer net}
\label{fig:singleWeights}
\end{figure}

The final weights for the single layer net are shown in Fig. \ref{fig:singleWeights}. We see that the net is placing emphasis on the bridge forming between the two galaxies as well as on the tidal distortions around the edges. Interestingly, the net also thinks that the core of the left galaxy is extremely important. This may be due to the fact that all of our model images are positioned roughly the same way, and in every image there is a bright spot marking the center of a galaxy at roughly the hotspot location shown in Fig. \ref{fig:singleWeights}.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.75\linewidth]{./Images/convWeight1.png}}
\caption{Visualization of weights for the first convolution layer}
\label{fig:convWeight1}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.75\linewidth]{./Images/convWeight2.png}}
\caption{Visualization of weights for the second convolution layer}
\label{fig:convWeight2}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.75\linewidth]{./Images/layer1activations.png}}
\caption{Visualization of network activations for the first convolution layer}
\label{fig:layer1activations}
\end{figure}

Fig. \ref{fig:convWeight1} and Fig. \ref{fig:convWeight2} show the weights for the first and second convolution layers respectively. However, it is hard to glean and useful information from just these weights on their own. That is why we have shown the activations of units in the first layer in Fig. \ref{fig:layer1activations}. We can see that for this specific activation, the net was processing a model that was very similar to the target image. We can see units that are picking up the major features: galactic cores, tidal distortions, and the bridge. We can also plainly see the units that are detecting the edges of the galaxies, as well as some units that aren't really being utilized.

@@

Another factor to consider is the noise associated with the human scores. As a citizen scientist project, the models in the Galaxy Zoo: Mergers data set were ranked by people with minimal training. There are also no checks in place to prevent against people clicking though models without consideration, artificially inflating or deflating their scores. We must also acknowledge the randomness of the tournament system. It is entirely possible that some models were "unlucky" and went against rounds of exclusively good models, causing them to be scored lower than they actually should have or vice versa.

@@

Future work could pertain to the expansion of the convolutional net to include more layers. Training with these extra layers and units would necessitate a larger data set, hopefully with a more even distribution of model quality. We believe that such a net would obtain better results than either of the nets described in this paper.  Also, the nets we created for this paper could be applied to the other 61 galaxy pairs, and, with enough training, possibly eliminate the need for further human rankings. This would allow for new models to be created and scored much faster than they have been previously.
